\begin{sloppypar}
\section{Acknowledgements}

It has been a long road to get to this point. Three years working through community college, another four for undergrad at VT, and another two for graduate school at VT. There are many people who have made a difference along the way, especially in this final stretch.

I want to thank my committee members, Dr. Alfred Wicks, Dr. Alan Asbeck, and Dr. Steve Southward for their guidance and being a part of my committee. I want to give an extra thank you to Dr. Wicks for the guidance you have provided, as well as always encour- aging me to do the things that I did not prefer to do that made me a better engineer. I owe a huge thank you to all those in the Mechatronics Lab. The amount of knowledge in the lab is immense and never ceases to amaze me. You all have made work enjoyable and I hope those in the next workplace are just as fun.

I want to thank my ?Intro to Thermodynamics? Professor, Dr. Anthony ?Tony? Ferrar. You were an excellent mentor when it came to discussing the decision on whether or not to pursue a graduate degree. Your passion for teaching, emphasis on education, and advice really influenced me continuing on to graduate school. I also want to thank my best friend, Katey Smith. Since meeting you sophomore year, you have continued to inspire me. You were another individual who encouraged me to attend graduate school, and in doing so, further inspired me to be the best that I can be.

Last, but certainly not least, thank you to my parents Denver C. and Norma, and my siblings Austin, Dylan, and Daniel. I could not have had a better family to inspire, support, and encourage me through undergrad, graduate school, and life in general. It is through your love and support that I am who I am today.

\end{sloppypar}